### 2015-03-12 rebuttal.txt

* Reviewer 1
** Anomaly detection
The paper describes an approach to fuse reports from IDSes; it does not do anomaly detection. MIFD fuses IDS reports from both anomaly- and signature-based IDSes. Perhaps confusion arises from System Z+'s use of the term "surprise" for its measure, which goes up as likelihood goes down.
** Code and data are not available
The data will be made available on the web. The code could be made available under limited license for research purposes, making reproduction and comparison feasible.
** Comparison
While this would be desirable, existing IDS fusion techniques do not share an input format or output definition. Most simply cluster and do not categorize hypotheses by posterior likelihood. However, it would be simple for other researchers to adapt their systems to our data sets: our synthetic reports would be simple to translate into other input formats.
* Reviewer 11
** Clarifications
*** Three sensors
You'd noted in the review that we "used three sensors for possible fusion." That's not exactly right --- although we do use a ratio of three sensors detecting each attack in most experiments, we vary that ratio in the first experiment.
*** Removing event hypotheses and sensor reports
We'd intended this remark as something of an aside, since (as the paper states) we are not actually doing this cleanup in the system under experimentation.  
The volume of data which IDSs encounter necessitates some sort of garbage collection. You are correct that the timing of such clean up must be carefully considered. In the full system, hypotheses are only purged after an interval since receipt of the last related IDS report. All reports and hypotheses are archived in a database.
It would probably be best to simply cut this minor aside from the paper, since garbage-collection plays no role in these experiments.
** Justification for choice of parameter settings
In all cases, the initial settings for the configuration parameters are both typical values for an IDS, and consistent with Z+'s assumptions. The experiments vary these values in ways which we anticipate would be worse for MIFD's performance, to examine our expected performance both under typical conditions, and under less typical conditions approaching worst-case.
** Relation to boosting
Boosting does provide an alternative method for fusion, but is not appropriate to IDS fusion. Boosting is based on learning, but IDS fusion problems do not admit use of ML: we do not get labeled data of attacks, nor do we get reference data showing systems operating without attacks. We will add a citation to papers about the failure of ML for IDS. These challenges (see [Sommer&Paxson,2010;Gates&Taylor,2006] on the challenges of ML in IDS, full cites available upon request) account for our adoption of a qualitative, non-adaptive framework. Also note that different IDSes do not share a single "ontology" of events; part of the function of MIFD's clustering is to align reports with different frames of reference.
** Other suggestions
Thank you for the many thoughtful suggestions for clarification.  We will edit the text to address all of these issues.
* Reviewer 4
** Novelty, technical quality, and significance
We respectfully disagree with this review's judgment about the novelty of our work.
It is true that System Z+ is well-studied in the literature, and /proposals/ to apply it to inference problems are common. However, we reviewed the 250+ papers citing the Z+ AIJ paper on Google Scholar (We will make the list of citations available upon request), and found no other paper describing an application of Z+ to a real-world problem. Accordingly, we assert that studying the application, and more to the point, the range of applicability, of System Z+ is novel.
Further, in order to apply an approximation technique such as Z+, one must have a clear understanding of when it will work, when it will fail, and how it will degrade from one to the other. Z+ is based on an idealization of uncertain reasoning, and it is necessary to study how it will work when its simplifying assumptions are violated. Our experiments studied exactly this --- beginning with assumptions in line with both the particular application of IDS and with Z+, and then diverging from them --- not "testing for the sake of testing."
There are numerous useful points of comparison in the literature: Consider how naive Bayesian classification has been studied: Anecdotal experience that useful results were computed even when violating independence assumptions led to more systematic studies of the integrity of Bayes classification as the independence failed.  Heckerman and Horvitz's study of why confidence factors work is in a similar vein.  Another point of comparison is big-O analysis: while it is of great utility, there are many cases where the constant factors do matter, and the idealization provides misleading results. Failure to investigate such cases would hamper computer science as a whole.
In this case System Z+ has been believed to be a useful approximation to real probabilities, and the novelty here is to examine the performance of Z+ as its assumptions are increasingly violated (with particular application to sensor fusion).
If we aren't willing to accept research that explores why a technique works or fails to work in practice, we doom applications work to be prescientific. Any single application can be made to work with a large enough investment of one-off labor: generalizing and validating requires follow-up.
Finally, we stress that our results are relevant to sensor fusion applications in general, not just IDS fusion.
We will improve the clarity of these introductory points in the final version of the paper.
** Quality of writing
Although it is difficult to address the non-specific claim of poor writing, our incorporation of the specific suggestions from the above reviews may address this reviewer's concerns.

* COMMENT Uses of System Z+
We have looked at the 250+ citations of G&P's AIJ paper on System Z+. Of these
citations, only the following show an application of the technique. And none are
to actual real-world applications. Accordingly, we can challenge the claim that
this is not novel.
+ Approximating MDP in [[http://pdf.aminer.org/000/387/692/faster_heuristic_search_algorithms_for_planning_with_uncertainty_and_full.pdf][Bonet and Geffner]].  Same technique used in
  [[http://juban.free.fr/hp/publications/challenge_pomdp.pdf][The Challenge of Solving POMDPs for Control, Monitoring and Repair of Complex Systems]].
+ Plan recognition, [[http://www.aaai.org/ocs/index.php/AAAI/AAAI10/paper/download/1821/2160][Ramirez&Geffner]]
+ (possibly) [[http://link.springer.com/chapter/10.1007/978-3-319-02621-3_11][Diagnosing Dependent Action Delays in Temporal Multiagent Plans]]

* COMMENT other notes:
+ From description of clustering:
  Note
  that clustering does not itself generate a single output; clustering
  is in fact the first step to generate all of the possible
  hypotheses. The separate step of assessment assigns qualitative
  probabilities to the hypotheses. Even then, assessment might not
  produce a /single/ output; it may in fact be more than one event
  which causes the observed reports, or we may hypothesize different
  events with equal likelihood.

  We'll describe the IDS fusion problem more generally.
+ Definition of MIFD in abstract.
+ Positioning of figures on the same page as referenced
+ Axis labels in Figures 3-7.
+ Readability of Figure 6.

** Reviewer 11's other suggestions
+ Defining benign event hypotheses vs. attack event hypotheses.
+ Defining complex event hypotheses. Briefly, these refer to the case
  where a hypothesized event is taken as evidence for another
  hypothesized event.  Since we do not use these in the current experiments,
  we may drop this remark from the final paper.
+ Better define the notation used in table of System Z+ rules. \omega
  is a possible world; \phi\in\omega is the same as \omega\models\phi.
+ Clustering. MIFD generates event hypotheses for incoming sensor
  reports based on its model of attacks and sensors.
  In general, clustering will generate multiple hypotheses for a single report,
  and multiple reports may support a single hypothesis.
+ Suggestions to the intro/related work balance in "Intrusion
  Detection Fusion" section, and comparison to boosting.

* COMMENT Possible note
They have, counting extremely generously, 2 application-type papers in UAI 2013,
out of a total of 73.  It's tempting to raise this, but I'm not sure that I
care, because I suspect I'd rather have this paper accepted at AAAI instead of
UAI.

# Local Variables:
# mode: org
# End:

### 2015-03-12 ids-fusion.tex
Getting under 6,000 words

Existing \idses are not designed to work together as part of a
suite of sensors.  Instead, each program generates a separate,
often voluminous, stream of reports; fusing them into a coherent 
overview is left as an exercise for the user. 
Ideally, network administrators would have a suite of different \idses active,
since different \ids approaches --- network (NIDS) vs.\
host-based (HIDS), signature vs.\ anomaly-based --- bring different
strengths and weaknesses.
%%
%% Hm, can we just get rid of the details NIDS/HIDS and
%% signature/anomaly comparisons, and keep just the takeaway? I don't
%% believe we refer to them after this. 
%%
Briefly, more accurate \idses have significantly higher software
administration burdens, and there is an inevitable tradeoff between
false positives and false negatives.
%%
%%Some systems aim to overcome the limitations of existing \idses by assembling 
%%a suite of
%%sensors.  This can be a very efficient way to overcome the problem
%%of false positives, but relies crucially on finding sensors that fail
%%relatively independently.  
%%
%% 
%% NIDS systems are easy to deploy; from only one
%% or two locations, they can watch all relevant traffic.  Unfortunately, they also have
%% substantial problems with false positives and false negatives, because they
%% don't ``know'' the meaning of the traffic they see.  Often they must draw
%% conclusions based only on information in packet headers (although some
%% systems do attempt to reconstruct higher level protocols from packet data),
%% and more extensive reasoning about traffic either would slow down the
%% network, or must ignore some packets altogether.
%% A HIDS may take into account much more information about the state
%% of a defended system, but installing HIDS pervasively involves deploying and
%% configuring much more software.  Typically HIDS are installed on only the most
%% critical assets.
%% 
%% Signature-based systems attempt to match patterns of known bad behavior.  Such
%% \idses are plagued by false negatives, both because of novel attacks for which
%% there are no patterns to match, and because of known %knowledgeable attackers take
%% countermeasures against signature identification (e.g.\ encrypting malware, or
%% permuting its structure).  Anomaly detectors are prone to false
%% positives: anomalies are often benignly anomalous,
%% not maliciously so.  Detectors often believe there is an
%% anomaly when none exists because computer usage patterns are
%% notoriously difficult to learn: they are often non-stationary, they vary
%% substantially from location-to-location, etc.
%% \draft{Add citations of papers on the challenges of anomaly detection.}

The most substantial challenge in managing \idses is the information overload
that they can impose.
Much of this overload comes from the high false positive rate.  This rate is
partly due to
inaccurate sensors.
Another problem is the ``base rate fallacy''~\cite{Axelsson:1999:BFI:319709.319710}:
in intrusion detection, as in
other applications where very unlikely events must be detected, even a seemingly
accurate sensor may yield too many false positives.  Axelsson gives the example
of a 99\% accurate test detecting a disease that strikes only 1/10,000
patients.  The probability of having the disease given a positive test result is
only 1\%, although the probability of the sensor labeling correctly is 99\%.
{\ids} users regularly either ignore or partially disable them, unable to absorb
massive streams of false alarms:
``Users attending an 'ABCs of IDS' event at London's City University yesterday
  said more the 80 per cent of the alerts they received were false, with one
  citing 60 alerts he had received about non-existent problems that morning at
  0300''~\cite{Register}.
Recently, Target is reported to have ignored warnings about the
data breach that resulted in theft of millions of credit
cards~\cite{TargetIgnoredIDS}:
``They are bombarded with alerts. They get so many that they just don't respond
to everything''~\cite{finkle14:_target}.
Figure
\ref{fig:workloadReduction} gives a sense of the gravity of this
problem, showing how our earlier system was able to winnow
the 
flow of reports in a small corporate network~\anoncite{goldman:09Scyllarus}.
Data reduction, in addition to building a comprehensive overview
and overcoming false positives and negatives, must be a goal of \ids fusion.
% \begin{figure*}[t]
%   \begin{tabular}{c}
%     \ifthenelse{\boolean{blackAndWhite}}{%
%       \includegraphics[width=.7\textwidth]{figures/funnel-bw.pdf} }{%
%     \includegraphics[width=.7\textwidth]{figures/funnel.pdf}} \\
%     \ifthenelse{\boolean{blackAndWhite}}{%
%         \includegraphics[width=.7\textwidth]{figures/funnel-graph-bw} }{%
%             \includegraphics[width=.7\textwidth]{figures/funnel-graph} } 
%   \end{tabular}
%   \centering
%   \caption{Scyllarus workload reduction~\anoncite{goldman:09Scyllarus}.}
%   \label{fig:workloadReduction}
% \end{figure*}
\begin{figure}[t]
    \ifthenelse{\boolean{blackAndWhite}}{%
      \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf} }{%
    \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf}} 
  \centering
  \caption{Scyllarus workload reduction~\anoncite{goldman:09Scyllarus}.}
  \label{fig:workloadReduction}
\end{figure}

@@

\paragraph{Related work.}
SecurityFocus has developed the
Attack Registry and Intelligence Service~\shortcite[ARIS]{ARIS}.
Its extractor consolidates {\ids} reports from four different
{\idses} into XML, and presents them in an incident
console.  However it makes no attempts to fuse the reports, nor weigh
evidence for and against them.
MetaSTAT is a fusion system built on a set of STAT-based
{\idses}~\cite{vigna01:designing}.  
STAT is signature-based, and detects events by matching
against extended finite-state event models.  MetaSTAT uses
finite-state models of across-sensor events to consume events
from lower-level sensors at a higher level,
but does not attempt to judge the plausibility of different
events.
EMERALD/eBayes~\cite{raid2001-pac} fusion is the most similar to our systems.
Their sensors are Bayes net-based, and the correlation approach
allows ``upstream'' sensors to adjust the priors on ``downstream''
sensors.
Its fusion is limited to clustering alerts that meet a
similarity criterion; they do not have models of high-level events like
ours (see below).  To the best of our knowledge, they do not
address the difficult issues of acquiring probability parameters for \ids fusion.
The Prelude IDS's Correlator allows users to analyze reports sent to Prelude 
from compatible IDSes~\cite{PreludeCor} following user-provided rules.  Its function is closest to
our clustering subsystem, but knowledge resides in stateful 
rules instead of an ontology of attacks. 
The Arcsight Enterprise Security Manager~\cite{ArcsightEsm},
also ties correlated IDS reports to an installation's security goals
and vulnerability information.

>>>>

Existing \idses are not designed to work together as part of a
suite of sensors.  Instead, each program generates a separate,
often voluminous, stream of reports; fusing them into a coherent 
overview is left
% TODO restore to QR15
%as an exercise for
 to
the user. 
Ideally, network administrators would have a suite of different \idses active,
since different \ids approaches
% TODO restore to QR15
% --- network (NIDS) vs.\
% host-based (HIDS), signature vs.\ anomaly-based --- 
bring different
strengths and weaknesses.
%%
%% Hm, can we just get rid of the details NIDS/HIDS and
%% signature/anomaly comparisons, and keep just the takeaway? I don't
%% believe we refer to them after this. 
%%
Briefly, more accurate \idses have significantly higher software
administration burdens, and there is an inevitable tradeoff between
false positives and false negatives.
%%
%%Some systems aim to overcome the limitations of existing \idses by assembling 
%%a suite of
%%sensors.  This can be a very efficient way to overcome the problem
%%of false positives, but relies crucially on finding sensors that fail
%%relatively independently.  
%%
%% 
%% NIDS systems are easy to deploy; from only one
%% or two locations, they can watch all relevant traffic.  Unfortunately, they also have
%% substantial problems with false positives and false negatives, because they
%% don't ``know'' the meaning of the traffic they see.  Often they must draw
%% conclusions based only on information in packet headers (although some
%% systems do attempt to reconstruct higher level protocols from packet data),
%% and more extensive reasoning about traffic either would slow down the
%% network, or must ignore some packets altogether.
%% A HIDS may take into account much more information about the state
%% of a defended system, but installing HIDS pervasively involves deploying and
%% configuring much more software.  Typically HIDS are installed on only the most
%% critical assets.
%% 
%% Signature-based systems attempt to match patterns of known bad behavior.  Such
%% \idses are plagued by false negatives, both because of novel attacks for which
%% there are no patterns to match, and because of known %knowledgeable attackers take
%% countermeasures against signature identification (e.g.\ encrypting malware, or
%% permuting its structure).  Anomaly detectors are prone to false
%% positives: anomalies are often benignly anomalous,
%% not maliciously so.  Detectors often believe there is an
%% anomaly when none exists because computer usage patterns are
%% notoriously difficult to learn: they are often non-stationary, they vary
%% substantially from location-to-location, etc.
%% \draft{Add citations of papers on the challenges of anomaly detection.}

The most substantial challenge in managing \idses is the information overload
that they can impose.
Much of this overload comes from the high false positive rate.  This rate is
partly due to
inaccurate sensors.
Another problem is the ``base rate fallacy''~\cite{Axelsson:1999:BFI:319709.319710}:
in intrusion detection, as in
other applications where very unlikely events must be detected, even a seemingly
accurate sensor may yield too many false positives.  Axelsson gives the example
of a 99\% accurate test detecting a disease that strikes only 1/10,000
patients.  The probability of having the disease given a positive test result is
only 1\%.
% %% This next bit seem redundant.
%, although the probability of the sensor labeling correctly is 99\%.
{\ids} users regularly either ignore or partially disable them, unable to absorb
massive streams of false alarms:%
%% TODO Restore for QR'15
%``Users attending an 'ABCs of IDS' event at London's City University yesterday
%  said more the 80 per cent of the alerts they received were false, with one
%  citing 60 alerts he had received about non-existent problems that morning at
%  0300''
~\cite{Register}.
Recently, Target is reported to have ignored warnings about the
data breach that resulted in theft of millions of credit
cards~\cite{TargetIgnoredIDS}:
``They are bombarded with alerts. They get so many that they just don't respond
to everything''~\cite{finkle14:_target}.
Figure
\ref{fig:workloadReduction} gives a sense of the gravity of this
problem, showing how our earlier system was able to winnow
the 
flow of reports in a small corporate network~\anoncite{goldman:09Scyllarus}.
Data reduction must join building a comprehensive overview
and overcoming false positives and negatives as goals of \ids fusion.
\begin{figure}[t]
    \ifthenelse{\boolean{blackAndWhite}}{%
      \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf} }{%
    \includegraphics[width=.45\textwidth]{figures/funnel-dup-cropped.pdf}} 
  \centering
  \caption{Scyllarus workload reduction%
% Squash citation here; cited in sentence referencing figure.
%~\anoncite{goldman:09Scyllarus}
.}
  \label{fig:workloadReduction}
\end{figure}

@@

\paragraph{Related work.}
%% TODO Restore for QR'15
%SecurityFocus has developed the
%Attack Registry and Intelligence Service~\shortcite[ARIS]{ARIS}.
%Its extractor consolidates {\ids} reports from four different
%{\idses} into XML, and presents them in an incident
%console.  However it makes no attempts to fuse the reports, nor weigh
%evidence for and against them.
%
%% TODO Restore full version for QR'15
STAT and MetaSTAT~\cite{vigna01:designing}
use finite-state models to detect and fuse events,
but do not attempt to judge the plausibility of different
events.
%MetaSTAT is a fusion system built on a set of STAT-based
%{\idses}~\cite{vigna01:designing}.  
%STAT is signature-based, and detects events by matching
%against extended finite-state event models.
%MetaSTAT uses
%finite-state models of across-sensor events to consume events
%from lower-level sensors at a higher level,
%but does not attempt to judge the plausibility of different
%events.
EMERALD/eBayes~\cite{raid2001-pac} fusion is the most similar to our systems.
Their sensors are Bayes net-based, and the correlation approach
allows ``upstream'' sensors to adjust the priors on ``downstream''
sensors.
Its fusion is limited to clustering alerts that meet a
similarity criterion; they do not have models of high-level events like
ours (see below).  To the best of our knowledge, they do not
address the difficult issues of acquiring probability parameters for \ids fusion.
The Prelude IDS's Correlator
%% TODO Restore full version for QR'15
% allows users to analyze reports sent to Prelude 
%from compatible IDSes~\cite{PreludeCor} following user-provided
%rules.  Its function
is closest to
our clustering subsystem, but knowledge resides in stateful 
rules instead of an ontology of attacks. 
%% TODO Restore full version for QR'15
%The Arcsight Enterprise Security Manager~\cite{ArcsightEsm},
%also ties correlated IDS reports to an installation's security goals
%and vulnerability information.

### 2015-03-12 scyllarus-and-mifd.tex
Getting under 6,000 words

Our original system Scyllarus was an open system which performed IDS
fusion on a diverse set of third party \idses~\anoncite{goldman:discex2001,goldman:discex2001}.
Its successor
MIFD (Model-based Intrusion Fusion and Detection),
enhances Scyllarus as part of the STRATUS system's
integration of IDS fusion into a comprehensive suite for cyber defense
\anoncite{thayer13:_compar_strat_tactic_respon_cyber_threat}.
For simplicity we refer to our \ids fusion system as ``MIFD,'' but
except where we specify otherwise, our account applies to Scyllarus as well.

The first tasks performed by MIFD are
\emph{collection} and \emph{translation}: IDS reports
must be collected and presented to MIFD, and
must be translated into a common
sensor report data structure for processing.
We will not discuss these less interesting
preliminaries, except to mention that they
involve a substantial amount of data rectification.  There is no widely-accepted
common data format (the proposed IDMEF standard~\cite{IDMEF} has not caught on), nor
is there an accepted taxonomy for events or event roles (e.g., the widely used ``source''
and ``destination'' are not consistently applied).
These problems are exacerbated by the fact that intrusion detection ``systems''
are often simply a casually-assembled anthology of rules by different authors running in the same
framework.

@@

\ids rules detect indirect features of intrusions, but they typically
report only the intrusion that their designer believes has caused the feature.
This creates a number of problems, first and foremost that the
sensors have high false positive rates.
For example, a local software update server
may look like an attacker performing reconnaissance.
What's worse, some of the false positives are correlated: the normal
activity of a print server may be mis-detected as a scan by several
different sensors.
To handle simple sensor failures, MIFD associates with each sensor a false
positive likelihood.
But to address the correlated false positives such as the scanning example, we
introduce benign events, that can compete with attack and (simple) false
positive explanations for results.\footnote{Where possible, we try to introduce sensors that
can specifically detect the benign events. To return to our earlier example, we
might introduce a ``print server sensor'' to help disambiguate detections. We do
not address this issue in our experiments.}
% FIXME: Add a figure 2(c) -- or separately numbered figure -- where we have a
% benign event, explaining two of the sensor reports, as well as the two attack
% events. 
Another problem with indirect sensing is that the sensors are often imprecise:
the features that they detect often occur not only in the absence of the
advertised intrusion, but in the presence of \emph{other} intrusions with
similar characteristics.

MIFD also has \emph{complex} events that have component sub-events, such as a
phishing attack with component events phishing email and drive-by-download.
Our current experiments do not address the role of complex events, so we will
not discuss them further.

>>>>

Our original system Scyllarus
%% TODO Restore for QR'15
% was an open system which 
performed IDS
fusion on a diverse set of third party \idses~\anoncite{goldman:discex2001,goldman:discex2001}.
Its successor
MIFD (Model-based Intrusion Fusion and Detection),
enhances Scyllarus
%% TODO Restore for QR'15
% as part of the STRATUS system's integration of
 to integrate
IDS fusion into a comprehensive suite for cyber defense
\anoncite{thayer13:_compar_strat_tactic_respon_cyber_threat}.
For simplicity we refer to our \ids fusion system as ``MIFD,'' but
except where we specify otherwise, our account applies to Scyllarus as well.

The first tasks performed by MIFD are
\emph{collection} and \emph{translation}: IDS reports
must be collected and presented to MIFD, and
must be translated into a common
sensor report data structure for processing.
We will not discuss these less interesting
preliminaries, except to mention that they
involve a substantial amount of data rectification
%% TODO Restore for QR'15
 to address the lack of standardization for data formats and event taxonomies.
%.  There is no widely-accepted
%common data format (the proposed IDMEF standard~\cite{IDMEF} has not caught on), nor
%is there an accepted taxonomy for events or event roles (e.g., the widely used ``source''
%and ``destination'' are not consistently applied).
%These problems are exacerbated by the fact that intrusion detection ``systems''
%are often simply a casually-assembled anthology of rules by different authors running in the same
%framework.

@@

\ids rules detect indirect features of intrusions, but they typically
report only the intrusion that their designer believes has caused the feature.
This creates a number of problems, first and foremost that the
sensors have high false positive rates.
For example, a local software update server
may look like an attacker performing reconnaissance.
Worse, some false positives are correlated: the normal
activity of a print server may be mis-detected as a scan by several
different sensors.
To handle simple sensor failures, MIFD associates with each sensor a false
positive likelihood.
But to address the correlated false positives such as the scanning example, we
introduce benign events, that can compete with attack and (simple) false
positive explanations for results.\footnote{And where possible, we try to introduce sensors that
can specifically detect the benign events. 
%% TODO Restore for QR'15
%To return to our earlier example, we
%might introduce a ``print server sensor'' to help disambiguate detections. We do
%not address this issue in our experiments.
}
% FIXME: Add a figure 2(c) -- or separately numbered figure -- where we have a
% benign event, explaining two of the sensor reports, as well as the two attack
% events. 
Another problem with indirect sensing is that the sensors are often imprecise:
the features that they detect often occur not only in the absence of the
advertised intrusion, but in the presence of \emph{other} intrusions with
similar characteristics.

%% TODO Restore for QR'15 --- we'd earlier discussed
%% removing this paragraph anyway.
%MIFD also has \emph{complex} events that have component sub-events, such as a
%phishing attack with component events phishing email and drive-by-download.
%Our current experiments do not address the role of complex events, so we will
%not discuss them further.
